Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-25 Paper/ms.tex
Circular orbit --> cosine

\subsection{Parameters and Priors}
To fit a planet model to RV data, we need parameters to describe
the properties of each planet. For simplicity, we describe each planet by
five parameters: the orbital period $P_i$, the semi-amplitude (in metres
per second) of the RV signal $A_i$, the phase of the signal
$\phi_i$ (defined such that $\psi=0$ gives an RV signal whose maximum is at
$t=0$), the eccentricity $e_i$, and the ``viewing angle'' $\theta_i$
(also known as the longitude of the line of sight).

>>>>

\subsection{Parameters and Priors}
To fit a planet model to RV data, we need parameters to describe
the properties of each planet. For simplicity, we describe each planet by
five parameters: the orbital period $P_i$, the semi-amplitude (in metres
per second) of the RV signal $A_i$, the phase of the signal
$\phi_i$ (defined such that $\phi=0$ gives an RV signal whose maximum is at
$t=0$), the eccentricity $e_i$, and the ``viewing angle'' $\theta_i$
(also known as the longitude of the line of sight). We defined our parameters
such that in the limit of zero eccentricity, the RV signal of a planet
reduces to $A_i\cos\left(2\pi t/P_i + \phi_i\right)$.
